---
title: "Finalizing the dye hit grid"
output: html_notebook
---

We have called all hits for all screens. 
Before making the final figure, we should plot everything that was called as a hit (and not a hit), to double-check our calls and catch any errors. 
These will also serve a supplemental figures, likely

Also, we need to sort through the hits called as a "2", which means "some protein-responsive behavior, but not a cannonical, at-the-correct-temperature DSF-like transition. Some of these can be represented in the main heatmap as "alternative detections" but we want to make sure we don't put any trash in that category... 
```{r}
library(grid) # arranging the plots for saving
library(phytools) # used to create the hierarchical clustering graph, and define the dye hit order
library(tidyverse)
```

First, need to re-do the hierarchichal clustering on chemminer to include the three AW dyes 
```{r}
# https://chemminetools.ucr.edu/tools/list_jobs/
# OpenBabel descriptors also calculated and downloaded: 
chem_desc <- read_csv("output_ignore/dye_descriptors/Exp0810--20200408_open_babel_descriptors.csv") %>%
  pivot_longer(-cid, names_to = "desc", values_to = "value") %>%
  dplyr::rename(dye =  "cid")

clean_dye_names <- function( vec ) {
  vec %>%
    gsub( "S.O.500X|SO500X", "SO5X", . ) %>% # low concentration SYPRO
    gsub( "S.O.5000X", "SO50X", . ) %>% # high concentration SYPRO, from old screens
    str_replace_all(. , "-", "") # remove hyphens from the names 
}

# these dyes include all of the ones for which we have both screening data and structures
#dye_order <- readRDS("output_ignore/dye_descriptors/Exp0810--dye_order.rds")
tre_1 <- read.newick(file = "output_ignore/dye_descriptors/clusteringtree (4).tre")
dye_order <- tre_1$tip.label%>% clean_dye_names() %>% factor(. , levels = .) 

dye_order <- tibble(
              dye_order = dye_order,
              order_numeric = c(1:length(dye_order))
            )

remove_screens <- c("Ds00009--0p01_TritonX100_in_P1", "Ds00011--Tau_P301S", "Exp0618--OLF", "Exp0707--DDM_buffer", "Exp0729--Tau_mi_diamond_10uM", "Exp0730--Tau_ms_diamond", "Exp0734--Tau_mi_diamond_1uM") # screens which we aren't going to consider in the paper

# read in and label all dye hits
dye_hits <- read_csv("output_ignore/hit_definitions/Exp0810--20200404_all_screen_hits_v3.csv") %>%
            pivot_longer(-c(comments, dye, `buffer too bad?`, reject_buffer, maxed_out, protein_sensitive), names_to = "screen", values_to = "value")  %>%
            mutate(dye_f = factor(.$dye, levels = dye_order$dye_order )) %>%
            filter(! screen %in% remove_screens) %>%
            mutate_at("value", gsub, pattern = 1, replacement = 10) %>%
            mutate_at("value", gsub, pattern = 2, replacement = 5) %>%
            mutate_at("value", as.numeric) %>%
            mutate_at("screen", gsub, pattern = "NHR32LBD", replacement = "NHR23LBD") %>%
            filter(! dye %in% c("SO5X", "SO50X")) %>% # keep only the "SYPRO" definition, which combines any SYPRO concentration
            filter(! dye %in% c("DMSO", "AW131", "AW132", "AW134"))# remove the DMSO and SYPRO columns

head(dye_hits)
# read in the layouts to determine which dyes were tested in each screen
dye_hits %>%
  ggplot(aes(x = screen, y = dye_f, fill = value), color = NA) +
  geom_tile() +
  theme_bw() +
  #scale_fill_viridis_c()+
 # dsfworld_default +
  coord_flip() -> p
p
```
```{r}
layouts_per_screen <- read_csv("output_ignore/hit_definitions/Exp0810--layouts_to_screens.csv")
layouts_per_screen
dyes_in_screenx <- read_csv("output_ignore/hit_definitions/Exp0810--all_layouts.csv")

dyes_in_screen <- read_csv("output_ignore/hit_definitions/Exp0810--all_layouts.csv") %>%
                    pivot_longer(-plate, names_to = "column", values_to = "dye") %>%
                    mutate_at("dye", clean_dye_names) %>%
                    mutate_at("dye", gsub, pattern = "SO50X", replacement = "SYPRO") %>%
                    filter(! dye %in% c("DMSO", "AW131", "AW132", "AW134")) %>% # remove the DMSO and SYPRO columns
                    filter( dye %in% dye_hits$dye ) %>%
                    rename(daughter = "plate") %>%
                    full_join(layouts_per_screen, by = "daughter") %>%
                    rename(screen = "Screen") %>%
                    mutate("tested_dye" = rep(1, times = nrow(.)) ) %>%
                    select(-c(column, daughter)) %>%
                    group_by(screen) %>%
                    distinct(dye, .keep_all = TRUE) %>% # remove the duplicate dyes which result from the layouts in which dyes were screened at multiple concentrations
                    ungroup() %>%
                    pivot_wider(id_cols = screen, names_from = dye, values_from = tested_dye) %>%
                    mutate(SYPRO = rep(1, times = nrow(.))) %>% # SYPRO was always screened %>%
                    pivot_longer(-screen, names_to = "dye", values_to = "tested",values_drop_na = FALSE)

dyes_in_screen %>% filter(screen == "Exp0521--NHR23LBD")

dyes_in_screen %>%
  full_join(dye_hits, by = c("screen", "dye")) %>%
  filter( tested == 1 ) %>%
  filter( screen %in% dye_hits$screen) %>%
  ggplot(aes(x = screen, y = dye_f, fill = value), color = NA) +
  geom_tile() +
  theme_bw() +
  #scale_fill_viridis_c()+
 # dsfworld_default +
  coord_flip()

# http://www.sthda.com/english/wiki/wiki.php?id_contents=7930
# the necessary link to add the histogramssing grid arrange
# see within it
# # Marginal histogram plot
# ggMarginal(sp2 + theme_gray(), type = "histogram",
#            fill = "steelblue", col = "darkblue")
```

Plot all the hits, and all the not-hits, for each protein
Probably should do this as a grob?

```{r}
# here are some examples from  http://www.sthda.com/english/wiki/wiki.php?id_contents=7930

```

```{r}
# this works for arranging facets without distorting their widths if ncol or nrow is not identical between them
a <- qplot(1:10, rnorm(10), main = "a")
b <- qplot(1:10, rnorm(10), main = "b")
c <- qplot(1:10, rnorm(10), main = "c")

pdf("test_layouts.pdf", height = 11, width = 8.5, paper = "letter")
grid.newpage()
pushViewport(viewport(layout = grid.layout(3, 15))) 
# the number of rows is set by the total number of rows in all of the plots
# the number of columns is the maximum number of ncol in the facets (e.g. 15)

vplayout <- function(x, y) viewport(layout.pos.row = x, layout.pos.col = y)
print(a, vp = vplayout(1, 1:15))  # 1:number of rows in plot 1, 1:number of cols in this facet
print(b, vp = vplayout(2, 1:3)) # 1:number of rows in this facet, 1:number of cols in this facet
print(c, vp = vplayout(3, 2:10)) # 1:number of rows in this facet, 1:number of cols in this facet

## Stop writing to the PDF file
dev.off()
```

```{r}
# hits_filtered <- dyes_in_screen %>%
#                   full_join(dye_hits, by = c("screen", "dye")) %>%
#                   filter( tested == 1 ) %>%
#                   filter( screen %in% dye_hits$screen)
  
# for a given protein, determine how many hit dyes are present in each
facet_no_y_theme <- theme( # for the first hit-calling plot, the most austere
  text = element_text(size = 8),
  axis.title = element_blank(), # don't label the axes
  axis.text.x = element_text(angle = 45), # don't label the numbers on the axes
  axis.ticks = element_blank(), # dont have ticks
  #legend.position = "right", # put a legent on the right of the plot
  legend.position = "none", # put a legent on the right of the plot
  plot.title = element_text(lineheight=.8, face="bold", size = 12), # have a title
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  strip.background = element_blank(),
  panel.spacing.x = unit(0.1, "lines"),
  panel.spacing.y = unit(0.1, "lines"),
  aspect.ratio = 1,
    plot.margin = margin(0, 0, 0, 0, "cm")
)

facet_wrap_two_conc <- function(df_melt, title, ncol_set) {
  p <- ggplot(df_melt, aes(x = Temperature, # temperature on X
                           y = value, # RFU on y
                           color = channel_f, # colored by the state
                           linetype = type,
                           group = well_channel_type # group means series, as in, this defines the unique data sets
  )) +
    geom_line(size = 0.3, alpha = 0.8) + # change the line type depending on the dye concentration # linetype = df_melt$conc #
    facet_wrap(~dye, scales = "free", ncol = ncol_set) +
    #labs(title = title, color = "Channel") +
    theme_bw() +
    scale_color_manual( values = c("Cy5.5" = "#67000d", "Cy5" = "#a50f15", "ROX" = "#ef3b2c", "TAMRA" = "#f16913", "JOE" = "#74c476", "FAM" = "#2171b5")) +
    scale_linetype_manual(values = c("dashed", "solid")) +
    facet_no_y_theme
  
  p # return the plot
}

get_dims <- function( ndyes ) {
  nd_length <- ndyes %>% length()
  
  list(
    total_dyes  = nd_length,
    ncol = if (nd_length < 15 ) { nd_length } else { 15 },
    nrow = ceiling( nd_length/15)
  )
 
}

make_total_dims <- function( dim10, dim5, dim0 ) {
  total_rows <- dim10$nrow + dim5$nrow + dim0$nrow + 3 # for margins and a title
  ncols <- max( c(dim10$ncol, dim5$ncol, dim0$ncol)) + 2 # for margins
  
  list(total_rows = total_rows, # for margins and a title
       total_cols = ncols, 
       
       hits10_cols = c(2:(dim10$ncol+1)), # start at 2
       hits10_rows = c(2:(dim10$nrow+1)), # start at 2
       
       hits5_cols = c(2:(dim5$ncol+1)),  # start at 2
       hits5_rows = c((2+dim10$nrow):((1+dim10$nrow)+dim5$nrow)),
       
       hits0_cols = c(2:(dim0$ncol+1)),  # start at 2
       hits0_rows = c((total_rows-dim0$nrow-1):(total_rows-1)))
}

make_screen_summary <- function(path_to_data, screen_name, hits_filtered, ncol_set) {
  df_raw <- readRDS(path_to_data)
  
  hits <- hits_filtered %>% filter(screen == screen_name, tested == 1) 
  
  hits10 <- hits %>%  filter(value == 10 ) %>% .$dye  
  hits5 <- hits %>% filter(value == 5 ) %>% .$dye
  hits0 <- hits %>% filter(value == 0 ) %>% .$dye
  
  dims <- make_total_dims( get_dims(hits10), 
                           get_dims(hits5), 
                           get_dims(hits0) 
                           )
  
    p10 <- df_raw %>%
          filter(dye %in% hits10)  %>%
          unite("well_channel_type", c(well, channel, type), remove = FALSE) %>%
          facet_wrap_two_conc("Hits", ncol_set)

    p5 <- df_raw %>%
          filter(dye %in% hits5)  %>%
          unite("well_channel_type", c(well, channel, type), remove = FALSE) %>%
          facet_wrap_two_conc("Protein sensitive, not a hit", ncol_set)

    p0 <- df_raw %>%
          filter(dye %in% hits0)  %>%
          unite("well_channel_type", c(well, channel, type), remove = FALSE) %>%
          facet_wrap_two_conc("Not a hit", ncol_set)

pdf_name <- paste0("output_ignore/individual_processed_screens/hits_sorted/", screen_name, "_hits_sorted.pdf")
pdf(pdf_name, height= dims$total_rows+4, width = dims$total_cols+3)
grid.newpage()
pushViewport(viewport(layout = grid.layout(dims$total_rows+4, dims$total_cols)))
#pushViewport(viewport(layout = grid.layout(3+3, dims$total_cols)))
vplayout <- function(x, y) viewport(layout.pos.row = x, layout.pos.col = y)
grid.text(paste0(" \n  ", screen_name), vp = vplayout(1,3), hjust = c(0,0,0), gp = gpar(fontsize = 35))

grid.text("\n \n  Hit", vp = vplayout(2,3), hjust = c(0,0), gp = gpar(fontsize = 12))
print(p10, vp = vplayout(dims$hits10_rows+1, dims$hits10_cols ))  # 1:number of rows in plot 1, 1:number of cols in this facet

grid.text("  \n \n  Protein-sensitive, not a hit", vp = vplayout(dims$hits5_rows[[1]]+2-1,3), hjust = c(0,0,0), gp = gpar(fontsize = 12))
print(p5, vp = vplayout(dims$hits5_rows+1+1, dims$hits5_cols)) # 1:number of rows in this facet, 1:number of cols in this facet

grid.text("  \n \n  Not a hit", vp = vplayout(dims$hits0_rows[[1]]+3-1,3), hjust = c(0,0,0), gp = gpar(fontsize = 12))
print(p0, vp = vplayout(dims$hits0_rows+2+1, dims$hits0_cols)) # 1:number of rows in this facet, 1:number of cols in this facet

dev.off()
    

   
}
# processed_screens
# test <- make_screen_summary(path_to_data = "output_ignore/individual_processed_screens/Exp0620--NPAS2_PAS-A-processed.rds", 
#                             screen_name = "Exp0620--NPAS2_PAS-A",
#                                 protein = "NPAS2_PAS-A", 
#                                 hits_filtered = hits_filtered, 
#                                 ncol_set = 15)
 screen_paths[[5]]
test <- make_screen_summary(path_to_data = screen_paths[[5]], 
                            screen_name = screen_names[[5]],
                               # protein = "NPAS2_PAS-A", 
                                hits_filtered = hits_filtered, 
                                ncol_set = 15)

map2(screen_paths,  screen_names, make_screen_summary, hits_filtered = hits_filtered,  ncol_set = 15 )
```

```{r}
paste_second <- function( pattern_2 , pattern_1) {
  paste0(pattern_1, pattern_2 )
}

remove_screens <- c("Ds00009--0p01_TritonX100_in_P1", "Ds00011--Tau_P301S", "Exp0618--OLF", "Exp0707--DDM_buffer", "Exp0729--Tau_mi_diamond_10uM", "Exp0730--Tau_ms_diamond", "Exp0734--Tau_mi_diamond_1uM")
processed_screens <- c(
#"Ds00009--0p01_TritonX100_in_P1-processed.rds",
"Ds00010--Hsp72_SBD-processed.rds",
#"Ds00011--Tau_P301S-processed.rds",
"Exp0468--eIF2B_no_ISIB-processed.rds",
"Exp0469--eIF2B_with_ISRIB-processed.rds",
"Exp0486--Jdomain-processed.rds",
"Exp0497--Hsp60-processed.rds",
"Exp0503--FKBP12-processed.rds",
"Exp0507--Hsc70-processed.rds",
"Exp0521--NHR23LBD-processed.rds",
"Exp0535--free_aas_mix1_G-processed.rds",
"Exp0535--free_aas_mix2_CMLRG-processed.rds",
"Exp0535--free_aas_mix3_DESNQ-processed.rds",
"Exp0535--free_aas_mix4_AVILP-processed.rds",
"Exp0535--free_aas_mix5_FYWTH-processed.rds",
"Exp0595--ACD_domain_protein6-processed.rds",
"Exp0596--H104-FL-B5-pre-inc_protein5-processed.rds",
"Exp0598--FL-B5-pre-inc_protein2-processed.rds",
"Exp0610--B5_with_zinc-processed.rds",
"Exp0615--BSA-processed.rds",
"Exp0616--FKBP12-processed.rds",
#"Exp0618--OLF-processed.rds",
"Exp0619--PPIE-processed.rds",
"Exp0620--NPAS2_PAS-A-processed.rds",
"Exp0621--PER2_PAS-AB_wt-processed.rds",
"Exp0622--CLOCK_PASB_W362A-processed.rds",
"Exp0623--CP_BMAL1_PASB_W427A-processed.rds",
"Exp0624--HisPER2_AB_I324N-processed.rds",
"Exp0625--CP581_CBPKIX-processed.rds",
"Exp0626--CP547_p300_KIX-processed.rds",
"Exp0627--HisSUMO-processed.rds",
"Exp0628--Hsp10-processed.rds",
"Exp0629--HisGB1-processed.rds",
"Exp0630--Hsp60-processed.rds",
"Exp0650--His_NusA-processed.rds",
"Exp0671--GS_WT-processed.rds",
"Exp0672--GS_R341C-processed.rds",
"Exp0673--GS_324S-processed.rds",
"Exp0674--GS_324C-processed.rds",
"Exp0701--B5-pre-inc_phosphomim_protein_4-processed.rds",
#"Exp0707--DDM_buffer-processed.rds",
"Exp0710--Nucleosome-processed.rds",
"Exp0723--Retinoic_acid_receptor_alpha-processed.rds",
"Exp0727--Snf2h_dye_screen-processed.rds",
#"Exp0729--Tau_mi_diamond_10uM-processed.rds",
#"Exp0730--Tau_ms_diamond-processed.rds",
"Exp0731--OGlcNacTransferase-processed.rds",
"Exp0732--Widom_601_DNA-processed.rds")
#"Exp0734--Tau_mi_diamond_1uM-processed.rds") 

screen_paths <- processed_screens %>%
 map(paste_second,  "output_ignore/individual_processed_screens/") %>%
 unlist() %>%
 as.vector()

screen_names <- processed_screens %>%
  map(gsub, pattern = "-processed.rds", replacement = "") %>%
  unlist() %>%
  as.vector()

screen_names

```


```{r}
dims <- test$dims
p10 <- test$p10
p5 <- test$p5
p0 <- test$p0

screen_name <- "Exp0521--NHR23LBD"
pdf_name <- paste0(screen_name, "_hit_definitions.pdf")
pdf(pdf_name, height= dims$total_rows+4, width = dims$total_cols+3)
grid.newpage()
pushViewport(viewport(layout = grid.layout(dims$total_rows+4, dims$total_cols)))
#pushViewport(viewport(layout = grid.layout(3+3, dims$total_cols)))
vplayout <- function(x, y) viewport(layout.pos.row = x, layout.pos.col = y)
grid.text(paste0(" \n  ", screen_name), vp = vplayout(1,3), hjust = c(0,0,0), gp = gpar(fontsize = 20))
grid.text("\n \n  Hit", vp = vplayout(2,3), hjust = c(0,0), gp = gpar(fontsize = 12))
print(p10, vp = vplayout(dims$hits10_rows+1, dims$hits10_cols ))  # 1:number of rows in plot 1, 1:number of cols in this facet
grid.text("  \n \n  Protein-sensitive, not a hit", vp = vplayout(dims$hits5_rows[[1]]+2-1,3), hjust = c(0,0,0), gp = gpar(fontsize = 12))
print(p5, vp = vplayout(dims$hits5_rows+1+1, dims$hits5_cols)) # 1:number of rows in this facet, 1:number of cols in this facet
grid.text("  \n \n  Not a hit", vp = vplayout(dims$hits0_rows[[1]]+3-1,3), hjust = c(0,0,0), gp = gpar(fontsize = 12))
print(p0, vp = vplayout(dims$hits0_rows+2+1, dims$hits0_cols)) # 1:number of rows in this facet, 1:number of cols in this facet
dev.off()

```
```{r}
# push the same viewport several times
grid.newpage()
vp <- viewport(width=0.5, height=0.5)
pushViewport(vp)
#grid.rect(gp=gpar(col="blue"))
grid.text("Quarter of the device",
  y=unit(1, "npc") - unit(1, "lines"), gp=gpar(col="blue"))
grid.text("Top-level viewport",
  y=unit(1, "npc") - unit(1, "lines"), gp=gpar(col="grey"))

```

```{r}
dim10 <- test[[1]]
dim5 <- test[[2]]
dim0 <- test[[3]]

make_total_dims <- function( dim10, dim5, dim0 ) {
  total_rows <- dim10$nrow + dim5$nrow + dim0$nrow
  ncols <- max( c(dim10$ncol, dim5$ncol, dim0$ncol))
  
  list(total_rows = total_rows, 
       total_cols = ncols,
       hits10_cols = c(1:dim10$ncol),
       hits10_rows = c(1:dim10$nrow),
       
       hits5_cols = c(1:dim5$ncol),
       hits5_rows = c((1+dim10$nrow):dim5$nrow),
       
       hits0_cols = c(1,dim0$ncol),
       hit10_rows = c((total_rows-dim0$nrow):total_rows))
}

make_total_dims( dim10, dim5, dim0 )

```

```{r}
  hits <- hits_filtered %>%
          filter(screen == "Exp0620--NPAS2_PAS-A",
                 tested == 1) %>%
  filter(value == 10)
  hits
```







```{r}
dsfworld_default <- theme( # adapted from free amino acids hit call
  text = element_text(size = 10),
  axis.title.x = element_blank(),
  # axis.title.y = element_blank(),
  axis.text.y = element_text(size = 5),
 # axis.text.x = element_blank(),#element_text(angle = 45, vjust = 0.5),
 axis.text.x = element_text(angle = 90, vjust = 0.5),
  legend.position = "right",
  plot.title = element_text(lineheight=.8, face="bold", size = 12),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(), 
  strip.background = element_blank(),
 aspect.ratio = 1/1.618
)

# read in the raw data
# sort in to 1, 2, or neither (no hit)
# make the same plot for each one 

 # this one should work for everything?
facet_wrap_hits <- function(df_melt, title) {
  p <- ggplot(df_melt, aes(x = Temperature, # temperature on X
                           y = value, # RFU on y
                           color = channel_f, # colored by the state
                           linetype = type,
                           group = well_channel_type # group means series, as in, this defines the unique data sets
  )) +
    geom_line(size = 0.3, alpha = 0.8) + # change the line type depending on the dye concentration # linetype = df_melt$conc #
    facet_wrap(~dye, scales = "free", ncol = 15) +
    labs(title = title, color = "Channel") +
    theme_bw() +
    scale_color_manual( values = c("Cy5.5" = "#67000d", "Cy5" = "#a50f15", "ROX" = "#ef3b2c", "TAMRA" = "#f16913", "JOE" = "#74c476", "FAM" = "#2171b5")) +
    scale_linetype_manual(values = c("dashed", "solid")) +
    facet_no_y_theme
  
  p # return the plot
}
```


```{r}
# try with NHR23LBD and with Exp0650--His_NusA
NHR23LBD <- readRDS("output_ignore/individual_processed_screens/Exp0521--NHR23LBD-processed.rds") # has two concentrations per dye
NusA <- readRDS("output_ignore/individual_processed_screens/Exp0650--His_NusA-processed.rds") # has one concentration per dye
```
```{r}
# first, define which dyes fill what categories 

fetch_hit_dyes <- function( hit_df, screen_name, hit_value ) {
  hit_df %>%
  filter(value == hit_value,
         screen == screen_name) %>%
  select(dye) %>%
  as_vector() %>%
  as.character()
}

calc_width <- function( hit_vec ) {
  nrow <- hit_vec %>%
          length()
}

NHR23LBD_hits0 <- fetch_hit_dyes(hits_raw, "Exp0521--NHR32LBD", hit_value = 0)
NHR23LBD_hits1 <- fetch_hit_dyes(hits_raw, "Exp0521--NHR32LBD", hit_value = 1)
NHR23LBD_hits2 <- fetch_hit_dyes(hits_raw, "Exp0521--NHR32LBD", hit_value = 2)

```

```{r}
# make the plots
p1 <- NHR23LBD %>%
  unite("well_channel_type", c(well, channel, type), remove = FALSE) %>%
  filter(dye %in% NHR23LBD_hits1) %>%
  facet_wrap_hits(., "Primary hits (class 1)")
p1
p2 <- NHR23LBD %>%
  unite("well_channel_type", c(well, channel, type), remove = FALSE) %>%
  filter(dye %in% NHR23LBD_hits2) %>%
  facet_wrap_hits(., "Alternate hits (class 2)")

p0 <- NHR23LBD %>%
  unite("well_channel_type", c(well, channel, type), remove = FALSE) %>%
  filter(dye %in% NHR23LBD_hits0) %>%
  facet_wrap_hits(., "Not hits (class 0)")
  
p_all <- grid.arrange(p1, p2, p0, nrow = 3)

ggsave("test_grob.pdf", p1, width = 17, height = 25)
```

```{r}
grid.arrange(
  grobs = gl,
  widths = c(2, 1, 1),
  layout_matrix = rbind(c(1, 2, NA),
                        c(3, 3, 4))
)
```







