---
title: "Finalizing the dye hit grid"
output: html_notebook
---

We have called all hits for all screens. 
Before making the final figure, we should plot everything that was called as a hit (and not a hit), to double-check our calls and catch any errors. 
These will also serve a supplemental figures, likely

Also, we need to sort through the hits called as a "2", which means "some protein-responsive behavior, but not a cannonical, at-the-correct-temperature DSF-like transition. Some of these can be represented in the main heatmap as "alternative detections" but we want to make sure we don't put any trash in that category... 
```{r}
library(gridExtra)
library(phytools) # used to create the hierarchical clustering graph, and define the dye hit order
library(tidyverse)
```

First, need to re-do the hierarchichal clustering on chemminer to include the three AW dyes 
```{r}
# https://chemminetools.ucr.edu/tools/list_jobs/
# OpenBabel descriptors also calculated and downloaded: 
chem_desc <- read_csv("output_ignore/dye_descriptors/Exp0810--20200408_open_babel_descriptors.csv") %>%
  pivot_longer(-cid, names_to = "desc", values_to = "value") %>%
  dplyr::rename(dye =  "cid")

clean_dye_names <- function( vec ) {
  vec %>%
    gsub( "S.O.500X|SO500X", "SO5X", . ) %>% # low concentration SYPRO
    gsub( "S.O.5000X", "SO50X", . ) %>% # high concentration SYPRO, from old screens
    str_replace_all(. , "-", "") # remove hyphens from the names 
}

# these dyes include all of the ones for which we have both screening data and structures
#dye_order <- readRDS("output_ignore/dye_descriptors/Exp0810--dye_order.rds")
tre_1 <- read.newick(file = "output_ignore/dye_descriptors/clusteringtree (4).tre")
dye_order <- tre_1$tip.label%>% clean_dye_names() %>% factor(. , levels = .) 

dye_order <- tibble(
              dye_order = dye_order,
              order_numeric = c(1:length(dye_order))
            )

remove_screens <- c("Ds00009--0p01_TritonX100_in_P1", "Ds00011--Tau_P301S", "Exp0618--OLF", "Exp0707--DDM_buffer", "Exp0729--Tau_mi_diamond_10uM", "Exp0730--Tau_ms_diamond", "Exp0734--Tau_mi_diamond_1uM") # screens which we aren't going to consider in the paper

# read in and label all dye hits
dye_hits <- read_csv("output_ignore/hit_definitions/Exp0810--20200404_all_screen_hits_v3.csv") %>%
            pivot_longer(-c(comments, dye, `buffer too bad?`, reject_buffer, maxed_out, protein_sensitive), names_to = "screen", values_to = "value")  %>%
            mutate(dye_f = factor(.$dye, levels = dye_order$dye_order )) %>%
            filter(! screen %in% remove_screens) %>%
            mutate_at("value", gsub, pattern = 1, replacement = 10) %>%
            mutate_at("value", gsub, pattern = 2, replacement = 5) %>%
            mutate_at("value", as.numeric) %>%
            mutate_at("screen", gsub, pattern = "NHR32LBD", replacement = "NHR23LBD") %>%
            filter(! dye %in% c("SO5X", "SO50X")) %>% # keep only the "SYPRO" definition, which combines any SYPRO concentration
            filter(! dye %in% c("DMSO", "AW131", "AW132", "AW134"))# remove the DMSO and SYPRO columns

head(dye_hits)
# read in the layouts to determine which dyes were tested in each screen
dye_hits %>%
  ggplot(aes(x = screen, y = dye_f, fill = value), color = NA) +
  geom_tile() +
  theme_bw() +
  #scale_fill_viridis_c()+
 # dsfworld_default +
  coord_flip() -> p
p
```
```{r}
layouts_per_screen <- read_csv("output_ignore/hit_definitions/Exp0810--layouts_to_screens.csv")
layouts_per_screen
dyes_in_screenx <- read_csv("output_ignore/hit_definitions/Exp0810--all_layouts.csv")

dyes_in_screen <- read_csv("output_ignore/hit_definitions/Exp0810--all_layouts.csv") %>%
                    pivot_longer(-plate, names_to = "column", values_to = "dye") %>%
                    mutate_at("dye", clean_dye_names) %>%
                    mutate_at("dye", gsub, pattern = "SO50X", replacement = "SYPRO") %>%
                    filter(! dye %in% c("DMSO", "AW131", "AW132", "AW134")) %>% # remove the DMSO and SYPRO columns
                    filter( dye %in% dye_hits$dye ) %>%
                    rename(daughter = "plate") %>%
                    full_join(layouts_per_screen, by = "daughter") %>%
                    rename(screen = "Screen") %>%
                    mutate("tested_dye" = rep(1, times = nrow(.)) ) %>%
                    select(-c(column, daughter)) %>%
                    group_by(screen) %>%
                    distinct(dye, .keep_all = TRUE) %>% # remove the duplicate dyes which result from the layouts in which dyes were screened at multiple concentrations
                    ungroup() %>%
                    pivot_wider(id_cols = screen, names_from = dye, values_from = tested_dye) %>%
                    mutate(SYPRO = rep(1, times = nrow(.))) %>% # SYPRO was always screened %>%
                    pivot_longer(-screen, names_to = "dye", values_to = "tested",values_drop_na = FALSE)

dyes_in_screen %>% filter(screen == "Exp0521--NHR23LBD")

dyes_in_screen %>%
  full_join(dye_hits, by = c("screen", "dye")) %>%
  filter( tested == 1 ) %>%
  filter( screen %in% dye_hits$screen) %>%
  ggplot(aes(x = screen, y = dye_f, fill = value), color = NA) +
  geom_tile() +
  theme_bw() +
  #scale_fill_viridis_c()+
 # dsfworld_default +
  coord_flip()
```



First, read in the dye hit grid as it is now
```{r}
hits_raw <- read_csv("output_ignore/hit_definitions/Exp0810--20200404_all_screen_hits_v2.csv") %>%
                  pivot_longer(-c(comments, dye, `buffer too bad?`, reject_buffer, maxed_out, protein_sensitive), names_to = "screen", values_to = "value")  %>%
                  filter(dye %in% clustered_dyes) %>%
                   mutate(dye_f = factor(.$dye, levels = clustered_dyes)) 

any(is.na(hits_raw$dye_f) ) # no dyes should have NA in their factor ordering

# ultimately, these screens aren't going to be represented in the heat map (for various collaborator or "these don't tradiitonally melt anyway" reasons), but we'll carry them through these next steps anyway.   
# remove_screens <- c("Ds00009--0p01_TritonX100_in_P1", "Ds00011--Tau_P301S", "Exp0618--OLF", "Exp0707--DDM_buffer", "Exp0729--Tau_mi_diamond_10uM", "Exp0730--Tau_ms_diamond", "Exp0734--Tau_mi_diamond_1uM")
```
Plot all the hits, and all the not-hits, for each protein
Probably should do this as a grob?
```{r}
dsfworld_default <- theme( # adapted from free amino acids hit call
  text = element_text(size = 10),
  axis.title.x = element_blank(),
  # axis.title.y = element_blank(),
  axis.text.y = element_text(size = 5),
 # axis.text.x = element_blank(),#element_text(angle = 45, vjust = 0.5),
 axis.text.x = element_text(angle = 90, vjust = 0.5),
  legend.position = "right",
  plot.title = element_text(lineheight=.8, face="bold", size = 12),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(), 
  strip.background = element_blank(),
 aspect.ratio = 1/1.618
)

# read in the raw data
# sort in to 1, 2, or neither (no hit)
# make the same plot for each one 

 # this one should work for everything?
facet_wrap_hits <- function(df_melt, title) {
  p <- ggplot(df_melt, aes(x = Temperature, # temperature on X
                           y = value, # RFU on y
                           color = channel_f, # colored by the state
                           linetype = type,
                           group = well_channel_type # group means series, as in, this defines the unique data sets
  )) +
    geom_line(size = 0.3, alpha = 0.8) + # change the line type depending on the dye concentration # linetype = df_melt$conc #
    facet_wrap(~dye, scales = "free", ncol = 15) +
    labs(title = title, color = "Channel") +
    theme_bw() +
    scale_color_manual( values = c("Cy5.5" = "#67000d", "Cy5" = "#a50f15", "ROX" = "#ef3b2c", "TAMRA" = "#f16913", "JOE" = "#74c476", "FAM" = "#2171b5")) +
    scale_linetype_manual(values = c("dashed", "solid")) +
    facet_no_y_theme
  
  p # return the plot
}
```
```{r}
# try with NHR23LBD and with Exp0650--His_NusA
NHR23LBD <- readRDS("output_ignore/individual_processed_screens/Exp0521--NHR23LBD-processed.rds") # has two concentrations per dye
NusA <- readRDS("output_ignore/individual_processed_screens/Exp0650--His_NusA-processed.rds") # has one concentration per dye
```
```{r}
# first, define which dyes fill what categories 

fetch_hit_dyes <- function( hit_df, screen_name, hit_value ) {
  hit_df %>%
  filter(value == hit_value,
         screen == screen_name) %>%
  select(dye) %>%
  as_vector() %>%
  as.character()
}

calc_width <- function( hit_vec ) {
  nrow <- hit_vec %>%
          length()
}

NHR23LBD_hits0 <- fetch_hit_dyes(hits_raw, "Exp0521--NHR32LBD", hit_value = 0)
NHR23LBD_hits1 <- fetch_hit_dyes(hits_raw, "Exp0521--NHR32LBD", hit_value = 1)
NHR23LBD_hits2 <- fetch_hit_dyes(hits_raw, "Exp0521--NHR32LBD", hit_value = 2)

```

```{r}
# make the plots
p1 <- NHR23LBD %>%
  unite("well_channel_type", c(well, channel, type), remove = FALSE) %>%
  filter(dye %in% NHR23LBD_hits1) %>%
  facet_wrap_hits(., "Primary hits (class 1)")
p1
p2 <- NHR23LBD %>%
  unite("well_channel_type", c(well, channel, type), remove = FALSE) %>%
  filter(dye %in% NHR23LBD_hits2) %>%
  facet_wrap_hits(., "Alternate hits (class 2)")

p0 <- NHR23LBD %>%
  unite("well_channel_type", c(well, channel, type), remove = FALSE) %>%
  filter(dye %in% NHR23LBD_hits0) %>%
  facet_wrap_hits(., "Not hits (class 0)")
  
p_all <- grid.arrange(p1, p2, p0, nrow = 3)

ggsave("test_grob.pdf", p1, width = 17, height = 25)
```

```{r}
grid.arrange(
  grobs = gl,
  widths = c(2, 1, 1),
  layout_matrix = rbind(c(1, 2, NA),
                        c(3, 3, 4))
)
```







