---
title: "Isolating buffer data"
output: html_notebook
---

Here, we're reading in a manually-created excel file with data on all of the buffers which have been screened, and treating them as a set of negative controls for inclusion in the final heat map.

This is also where we will begin making some of the more final calls about which dyes get "rejected" for various buffer-alone reasons. 

```{r}
library(phytools) # to read in the newick tree
library(tidyverse)
```

```{r}
# read in the buffer information
buffer_components <- read.csv("output_ignore/Exp0810--20200405_screening_buffers_updated.csv") %>%
                  select_if(~sum(!is.na(.)) > 0) %>%
                  drop_na() %>%
                  rename(
                    screen = "Screen",
                    buffer = "Buffer",
                         buffer_component = "Buffer.component",
                         buffer_conc = "Buffer.concentration..mM.",
                         NaCl = "NaCl.mM",
                         TritonX100 = "Triton",
                        Tween20  = "Tween.20")
          
buffer_components$screen %>% table()

# do the first visualization with these
# Ds00010--Hsp72_SBD: Tween20
# Ds00009--0p01_TritonX100_in_P1 : Triton
# Exp0710--Nucleosome 1 mM EDTA

# Ds00010--Hsp72_SBD: EDTA
# Exp0732--Widom_601_DNA 1 mM EDTA

# Ds00010--Hsp72_SBD: 2% glycerol
# Ds00010--Hsp72_SBD: TCEP
#Exp0727--Snf2h_dye_screen: BME
#Exp0723--Retinoic_acid_receptor_alpha 5 mM DTT
```
```{r}
main_buffer_heat_map <- df_buffers %>%
  filter(screen %in% c("Ds00010--Hsp72_SBD: Tween20"))
```

read in the screens with unique buffers
```{r}
dsfworld_default <- theme( # adapted from free amino acids hit call
  text = element_text(size = 10),
  # axis.title.x = element_blank(),
  # axis.title.y = element_blank(),
  axis.text = element_text(size = 8),
  axis.text.x = element_text(angle = 45, vjust = 0.5),
  legend.position = "right",
  plot.title = element_text(lineheight=.8, face="bold", size = 12),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(), 
  strip.background = element_blank(),
  aspect.ratio = (1/1.618)
  # axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
  # axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid')
)

load_screen <- function( screen_name ) {
  dir("output_ignore/individual_processed_screens", full.names = T, pattern = screen_name ) %>%
    readRDS()
}

load_buffer_screen <- function( screen_name ) {
  load_screen(screen_name) %>%
    filter(type == "buffer") %>%
    filter(! dye %in% c("DMSO", "Empty"))
}

buffer_components <- df_buffers %>%
                  distinct(buffer, .keep_all = TRUE)

read_screens <- unique_buffers$screen %>% as.character() # these are the screens which should be read in 
read_screens
# test <- load_buffer_screen(read_screens[1])
# test %>% head()

# buffer_data_list <- lapply(read_screens, load_buffer_screen)
# write_rds(buffer_data_list, "output_ignore/Exp810--20200406_buffer_data.rds")
buffer_data_list <- readRDS("output_ignore/Exp810--20200406_buffer_data.rds")

```

```{r}
# read in the buffer component data
# buffer_comp <- read_csv("output_ignore/Exp0810--20200405_screening_buffers.csv") %>% rename(screen = "Screen")

buffer_df <- buffer_data_list %>% 
              bind_rows() %>%
             bind_rows( "Exp0625--CP581_CBPKIX-processed.rds" %>% load_buffer_screen())  # add a P1 screen, since the J domain screen was so long ago it doesn't have the full library

buffer_df$screen %>% table()

buffer_combined <- buffer_df %>%
               full_join( buffer_components, by = "screen" )

representative_buffers <- buffer_combined %>%
  filter(screen %in% c("Ds00010--Hsp72_SBD", "Ds00009--0p01_TritonX100_in_P1", "Exp0710--Nucleosome", "Exp0625--CP581_CBPKIX")) # for tween 20, triton, EDTA, and none of these things, respectively
```




```{r}
clean_dye_names2 <- function( vec ) {
  vec %>%
    gsub( "S.O.500X|SO500X|S.O.low|S.O. low|SYPRO", "SO5X", . ) %>% # low concentration SYPRO
    gsub( "S.O.5000X|S.O.high|S.O. high", "SO50X", . ) %>% # high concentration SYPRO, from old screens
    str_replace_all(. , "-", "") 
  
}

tre_1 <- read.newick(file = "output_ignore/clusteringtree (4).tre")
dye_order <- tre_1$tip.label%>% clean_dye_names2() %>% factor(. , levels = .) 


representative_buffers$screen %>% table()
# the summarized buffer dataframe
buffer_summary <- representative_buffers %>%
  group_by(well, channel, screen) %>%
  mutate( yspan = max(value) - min(value) ) %>%
  ungroup() %>%
  group_by(well, screen) %>%
  mutate(largest_yspan = yspan== max(yspan)) %>%
  ungroup() %>%
  mutate(dye_f = factor(.$dye, levels = dye_order )) %>%
  filter(! dye %in% c("DMSO", "Empty"))

buffer_summary$screen %>% table()
```

Make some plots to look at buffer behaviors 
```{r}

buffer_summary %>%
  filter(largest_yspan == TRUE) %>%
  filter(screen != "Ds00010--Hsp72_SBD") %>%
  filter(screen != "Exp0710--Nucleosome") %>%
  #filter(largest_)
  ggplot(aes(x = screen, y = dye_f, fill = yspan )) +
  geom_tile() +
  scale_fill_gradient(low = "#737373", high = "white")
 #  scale_fill_gradient2(low = "green", mid = "yellow", high = "red")

```

```{r}
buffer_summary %>%
  distinct(yspan, .keep_all = TRUE) -> t2


buffer_summary <- representative_buffers %>%
  group_by(well, channel, screen) %>%
  mutate( yspan = max(value) - min(value) ) %>%
  ungroup() 
representative_buffers$screen %>% table()

buffer_summary$screen %>% table
```


Make the protein hit heatmap.
First, read in the layouts to add NAs to the dyes not screened
```{r}
dyes_in_layouts <- read_csv("output_ignore/hit_definitions/Exp0810--all_layouts.csv") %>%
  pivot_longer(-plate, names_to = "column", values_to = "dye") %>%
  mutate_at("dye", clean_dye_names)

dyes_in_layouts
#layouts_per_screen <- read_csv("output_ignore/Exp0810--layouts_to_screens.csv")

```

Dye hit data
```{r}

dsfworld_default <- theme( # adapted from free amino acids hit call
  text = element_text(size = 10),
  axis.title.x = element_blank(),
  # axis.title.y = element_blank(),
  axis.text.y = element_text(size = 5),
 # axis.text.x = element_blank(),#element_text(angle = 45, vjust = 0.5),
 axis.text.x = element_text(angle = 90, vjust = 0.5),
  legend.position = "right",
  plot.title = element_text(lineheight=.8, face="bold", size = 12),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(), 
  strip.background = element_blank()
)

dye_hits <- read_csv("output_ignore/Exp0810--20200404_all_screen_hits_v2.csv") %>%
  pivot_longer(-c(comments, dye, `buffer too bad?`, reject_buffer, maxed_out, protein_sensitive), names_to = "screen", values_to = "value") %>%
    mutate(dye_f = factor(.$dye, levels = dye_order ))


remove_screens <- c("Ds00009--0p01_TritonX100_in_P1", "Ds00011--Tau_P301S", "Exp0618--OLF", "Exp0707--DDM_buffer", "Exp0729--Tau_mi_diamond_10uM", "Exp0730--Tau_ms_diamond", "Exp0734--Tau_mi_diamond_1uM")
# dye_hits %>% head()

dye_hits %>%
 filter(! screen %in% remove_screens) %>%
  ggplot(aes(x = screen, y = dye_f, fill = value), color = NA) +
  geom_tile() +
  theme_bw() +
  scale_fill_viridis_c()+
  dsfworld_default +
  coord_flip() -> p
p

ggsave("output_ignore/test_heatmap.pdf", p, width = 20, height = 5)
```


```{r}
t0 <- buffer_summary %>%
  distinct(yspan, .keep_all = TRUE) %>%
  filter(largest_yspan == TRUE) %>%
  filter(screen == "Exp0625--CP581_CBPKIX") 

t1 <- buffer_summary %>%
  distinct(yspan, .keep_all = TRUE) %>%
  filter(largest_yspan == TRUE) %>%
  filter(screen == "Exp0710--Nucleosome")
t0


t1
t0[!t0$dye %in% t1$dye,]

```





Load in the free amino acid data
From the functions from earlier in this experiment
```{r}
clean_dye_names <- function( vec ) {
  vec %>%
    gsub( "S.O.500X|SO500X|S.O.low|S.O. low", "SO5X", . ) %>% # low concentration SYPRO
    gsub( "S.O.5000X|S.O.high|S.O. high", "SO50X", . ) %>% # high concentration SYPRO, from old screens
    str_replace_all(. , "-", "") # remove hyphens from the names 
}



read_processed_screen <- function(paths_processed, screen_name, save_screen) {
  # paths_processed points to the folder which contains the processed data, e.g. ../Exp0615--20190628_BSA_606/intermediate
  # screen name is the index, e.g. Exp0615
  
  file_path <- dir(paths_processed, full.names = T, pattern = "buffer_and_protein_raw_data_m.rds")
 # screen_name <- substr(paths_processed, 4+3, 10+3)
  print(file_path)
  
 df <-  file_path %>%
          readRDS() %>%
              mutate(screen = rep(screen_name, times = nrow(.))) %>%
              #separate(screen, c("screen", "protein"), sep = "-", remove = TRUE) %>%
              mutate_at(c("dye"), clean_dye_names ) %>%
              select(-c("dye_conc", "dye_conc_type", "dye_conc_type_channel")) %>% # drop these, which reflect the old dye names
              unite("dye_conc", c(dye, conc), remove = FALSE) %>% # add these back in
              unite("dye_conc_type", c(dye_conc, type), remove = FALSE) %>%
              unite("dye_conc_type_channel", c(dye_conc_type, channel), remove = FALSE)  %>%

            # second, homogenize the column types
              mutate_at(vars(-Temperature, -value, -column, -conc, -channel_f), as.character) %>%
              mutate_at(vars(Temperature, value, column, conc), as.numeric)
 if ( save_screen == TRUE ) {
     write_rds(df, paste0("output_ignore/individual_processed_screens/", screen_name, "-processed.rds"))
 }

  df
}

```

```{r}
# read in all of the intermediate files
mix_folders <- c("../Exp0535--2090314_free_aas/mix1_G/Exp0804_reprocessed/intermediate",
                 "../Exp0535--2090314_free_aas/mix2_CMLRG/Exp0804_reprocessed/intermediate", 
                 "../Exp0535--2090314_free_aas/mix3_DESNQ/Exp0804_reprocessed/intermediate", 
                 "../Exp0535--2090314_free_aas/mix4_AVILP/Exp0804_reprocessed/intermediate", 
                 "../Exp0535--2090314_free_aas/mix5_FYWTH/Exp0804_reprocessed/intermediate")

aa_mixes <- c("G", "CMLRG", "DESNQ", "AVILP", "FYWTH")

read_and_label <- function( filepath, label ) {
  df <- readRDS(filepath) %>%
        mutate( aas = rep(label, times = nrow(.))) # append an amino-acid specific label
}

aas_screen_names <- c("Exp0535--free_aas_mix1_G",
                      "Exp0535--free_aas_mix2_CMLRG",
                      "Exp0535--free_aas_mix3_DESNQ",
                      "Exp0535--free_aas_mix4_AVILP",
                      "Exp0535--free_aas_mix5_FYWTH"
                      )

#mG <- read_processed_screen(mix_folders[[1]], screen_name = "Exp0535--free_aas_mix1_G", save_screen =TRUE)# try with one
aas <- map2(mix_folders, aas_screen_names, read_processed_screen, save_screen = TRUE)

```

```{r}
aas[[1]] %>% head()
```


# make visualizations for each of the backgrounds

Read in the tanimoto clustering data
```{r}
library(phytools)
tre_1 <- read.newick(file = "output_ignore/clusteringtree (4).tre")

dye_order <- tre_1$tip.label%>% clean_dye_names() %>% factor(. , levels = .) 

dye_order <- tibble(
  dye_order = dye_order,
  order_numeric = c(1:length(dye_order))
)

dye_order
```


```{r}
dsfworld_default <- theme( # adapted from free amino acids hit call
  text = element_text(size = 10),
  # axis.title.x = element_blank(),
  # axis.title.y = element_blank(),
  axis.text.y = element_text(size = 5),
  axis.text.x = element_text(angle = 0, vjust = 0.5, size = 10),
  legend.position = "right",
  plot.title = element_text(lineheight=.8, face="bold", size = 12),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(), 
  strip.background = element_blank(),
  aspect.ratio = (1/1.618)
  # axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
  # axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid')
)


aas_summary <- aas[[1]] %>%
  group_by(variable ) %>%
  mutate(max = max(value),
            min = min(value),
            yspan = max(value) - min(value)) %>%
  distinct(max, .keep_all = TRUE)

aas_summary %>%
  mutate(dye_order = factor(dye, levels = dye_order)) %>%
  ggplot(aes(x = dye_order, y = yspan, color = channel_f))+
  geom_point(alpha = 0.7) +
  scale_color_manual( values = c("Cy5.5" = "#67000d", "Cy5" = "#a50f15", "ROX" = "#ef3b2c", "TAMRA" = "#f16913", "JOE" = "#74c476", "FAM" = "#2171b5")) +
  theme_bw() +
  dsfworld_default +
  coord_flip() +
  labs(x = "Total RFU span over heating range", y = "", color = "Channel")

```
```{r}
condition_for_tre <- function( df, tree_names ){
  test_mat <-  df %>% ungroup() %>% select(yspan) %>% as.matrix() #%>%
  row.names(test_mat) <- df$dye %>% gsub("TW", "TW-", .)
  

missing_mat <- tre_1$tip.label[!tre_1$tip.label %in% aas_for_mat$dye]
mat_add <- matrix(0, nrow = length(missing_mat))
row.names(mat_add) <- missing_mat

rbind(test_mat, mat_add)
  
}

test_mat_cond <- condition_for_tre( aas_for_mat, tre_1$tip.label) 
#tre_1$tip.label <- tre_1$tip.label %>% clean_dye_names()
test_mat_cond

```

```{r}
aas_for_mat <- aas_summary %>%
  #full_join(tibble(dye = tre_1$tip.label), by = "dye") %>%
  ungroup() %>%
  group_by(well) %>%
  mutate(max_yspan = max(yspan)) %>%
  distinct(dye, .keep_all = TRUE) 
all(tre_1$tip.label %in% aas_for_mat$dye)

test_mat <-  aas_for_mat %>% ungroup() %>% select(yspan) %>% as.matrix() #%>%
row.names(test_mat) <- aas_for_mat$dye
test_mat %>% head()
test_mat

tre_1 <- read.newick(file = "output_ignore/clusteringtree (4).tre") 
tre_1_rename <- tre_1
#tre_1_rename$tip.label <- tre_1$tip.label %>% clean_dye_names()

colors<-colorRampPalette(colors=c("#f7fbff","#08306b"))(800)
pdf(file = "test_aas_heat_map.pdf", height = 80, width = 10) # save it
phylo.heatmap(tre_1, test_mat_cond, color = colors )
#phylo.heatmap(tre_1, class_1, color = colors )#, standardize=FALSE,lwd=3,
    #pts=FALSE)
dev.off()


tre_1$tip.label[!tre_1$tip.label %in% aas_for_mat$dye]

aas_for_mat$dye
```







Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

