---
title: "Making dye hit heat maps"
output: html_notebook
---


This notebook includes functions for making dye hit grid heat-maps.

```{r}
library(phytools)
library(tidyverse)
```


```{r}
# f*ck all of this making the heatmaps in ggplot
length(dye_tree$tip.label)
str(outmat)

X_dye <- fastBM(dye_tree, nsim=1)
str(X_dye)
str(outmat)

str(dye_tree)
str(tree)
pdf(file = "test_heatmap.pdf", height = 80, width = 10) # save it
phylo.heatmap(dye_tree, X_dye) #, color = color_t, standardize = FALSE,lwd=3,
    #pts=FALSE)
dev.off()
```

```{r}
for_heatmap <- function( df,  tree, var_name ) {
  dye_names_tree <- tree$tip.label
  
  df_for_mat <- df %>%
    mutate_at("dye", clean_dye_names ) %>%
    filter(dye %in% dye_names_tree)

    no_val <- tibble(dye = dye_names_tree[!dye_names_tree %in% df$dye],
                   value = rep(NA, length(dye_names_tree[!dye_names_tree %in% df$dye]))
                   )
    
    df_for_mat_all <- df_for_mat %>%
                      bind_rows(no_val) %>%
                      filter(dye %in% dye_names_tree) %>%
                      mutate(dye_f = factor(dye, levels =dye_names_tree )) %>%
                      arrange(desc(dye_f)) %>%
                      mutate("x_var" = rep(var_name, times = nrow(.)))
}

dye_order <- dye_tree$tip.label %>% clean_dye_names() %>% factor(. , levels = .) 


df_for_heatmap <- df_test %>%
                  for_heatmap(., dye_tree, var_name = "Glycine")

 ggplot(df_for_heatmap, aes(x = x_var, y = dye_f )) +
   geom_tile(data = df_for_heatmap %>% filter(is.na(value)), fill = NA) +
   geom_tile(data = df_for_heatmap %>% filter(!is.na(value)), aes(fill = value)) +
   theme_void()
```


Making heatmaps using ggplot, and the dye ordering from the newick tree. 

Making the dye hit grid heat maps

First, read in the dye layouts from the various screens, and add NAs to the dyes not screened. Currently, not-hits and dyes not screened are both zeroes in the hits sheet
```{r}
dyes_in_layouts <- read_csv("output_ignore/Exp0810--all_layouts.csv")

layouts_per_screen <- read_csv("output_ignore/Exp0810--layouts_to_screens.csv")
layouts_per_screen
```

```{r}

```



Then make the heatmaps for the buffers
```{r}
# make the buffer hit grid
buffer_hits_raw <- read_csv("output_ignore/Exp0810--20200404_all_screen_hits_v2.csv")


```





